Response to the defense feedback

### 2021-06-01 SupplementaryMaterial/Acknowledgments.tex
Updates from Overleaf

The members of my committee, Peng Liu, Sencun Zhu, Benjamin Hanrahan, and James Larus, provided helpful comments on my dissertation. Prof. Liu and Prof. Zhu greatly improved this dissertation with their comments from a security research aspect. Prof. Hanrahan and Prof. Larus helped me improve the grammar of my dissertation. Jim has a keen observation about Abacus. His comments are very close to the reviewers. However, I did not take his comments seriously at the very beginning.

@@

Finally, I would like to thank my parents for their continuous emotional and financial support. My parents always hope that I can find a job that is near to them. However, they still expressed their full support for me when I decided to come to U.S. as a graduate student.

>>>>

The members of my committee, Peng Liu, Sencun Zhu, Benjamin Hanrahan, and James Larus, provided helpful comments on my dissertation. Prof. Liu and Prof. Zhu greatly improved this dissertation with their comments from a security research angle. Prof. Hanrahan and Prof. Larus helped me improve the grammar of my dissertation. Jim is my last English teacher. I learned a lot on the written English from him.  His comments are also very close to what I get from reviewers later. However, I did not take his comments seriously at the very beginning.

@@

Finally, I would like to thank my parents for their continuous emotional and financial support. My parents always hope that I can study in a university that is near to them. However, they still expressed their full support for me when I decided to come to U.S. as a graduate student.
